### 2023-05-09 code/1_exclusions/1_exclusionsUS.Rmd
cogsci ready

```{r}
df.demog_metadata <- data.frame(
  country = c("US"),
  ppts_finished = c(length(unique(df.ppts_finished_E$subject))),
  ppts_att_check_excl = c(length(unique(df.ppts_finished_E$subject)) - length(unique(df.ppts_att_E$subject))), 
  ppts_after_att_check_excl = c(length(unique(df.ppts_att_E$subject))),
  ppts_non_native_speaker = c(paste(length(ppts_non_native_lang_E),"*")), 
  ppts_en_speaker = c("N/A"),
  ppts_vi_speaker = c(paste(length(ppts_vi_speaker_E),"*")), 
  ppts_zh_speaker = c(paste(length(ppts_zh_speaker_E),"*")), 
  ppts_lived_abroad = c(paste(length(ppts_lived_abroad_E),"*")), 
  ppts_oversea_exp = c(length(ppts_oversea_exp_E)),
  ppts_after_demog_excl = c(length(unique(df.resp_E_aft_demog$subject))))
# colnames(df.demog_metadata) <- c("Participants Finished", 
#                                  "Participants ")
```

>>>>

```{r}
df.demog_metadata <- data.frame(
  country = c("US"),
  ppts_finished = c(length(unique(df.ppts_finished_E$subject))),
  ppts_att_check_excl = c(length(unique(df.ppts_finished_E$subject)) - length(unique(df.ppts_att_E$subject))), 
  ppts_after_att_check_excl = c(length(unique(df.ppts_att_E$subject))),
  ppts_non_native_speaker = c(paste(length(ppts_non_native_lang_E),"*")), 
  ppts_en_speaker = c("N/A"),
  ppts_vi_speaker = c(paste(length(ppts_vi_speaker_E),"*")), 
  ppts_zh_speaker = c(paste(length(ppts_zh_speaker_E),"*")), 
  ppts_lived_abroad = c(paste(length(ppts_lived_abroad_E),"*")), 
  ppts_oversea_exp = c(length(ppts_oversea_exp_E)),
  ppts_after_demog_excl = c(length(unique(df.resp_E_aft_demog$subject))))
# colnames(df.demog_metadata) <- c("Participants Finished", "Participants ")
```

### 2023-05-09 code/1_exclusions_exploratory/1_exclusionsCN.Rmd
cogsci ready

>>>>

df.ppts_att_M <- df.resp_M %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "选择")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(correct_response = str_replace_all(correct_response, "“", "")) %>%
  mutate(correct_response = str_replace_all(correct_response, "”", "")) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarise(n_att_check_correct_M = sum(pass_att_check))

ggplot(data = df.ppts_att_M, 
       mapping = aes(x = n_att_check_correct_M)) + 
  geom_bar()+ 
  scale_x_discrete(limits=0:10, labels = 0:10)

### 2023-05-09 code/1_exclusions_exploratory/1_exclusionsUS.Rmd
cogsci ready

>>>>

df.ppts_att_E <- df.resp_E %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "Choose ")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarise(n_att_check_correct_E = sum(pass_att_check))

ggplot(data = df.ppts_att_E, 
       mapping = aes(x = n_att_check_correct_E)) + 
  geom_bar()+ 
  scale_x_discrete(limits=0:10, labels = 0:10)

### 2023-05-09 code/1_exclusions_exploratory/1_exclusionsVN.Rmd
cogsci ready

@@

df.resp_V_aft_attn <- df.resp_V %>%
  filter(subject %in% df.ppts_att_V$subject) #73

>>>>

df.ppts_att_V <- df.resp_V %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "Chọn ")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarise(n_att_check_correct_V = sum(pass_att_check))

ggplot(data = df.ppts_att_V, 
       mapping = aes(x = n_att_check_correct_V)) + 
  geom_bar()+ 
  scale_x_discrete(limits=0:10, labels = 0:10)

@@

df.ppts_att_E <- df.resp_E %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "Choose ")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarise(n_att_check_correct = sum(pass_att_check))

ggplot(data = df.ppts_att_E, 
       mapping = aes(x = n_att_check_correct)) + 
  geom_bar()+ 
  scale_x_discrete(limits=0:10, labels = 0:10)df.resp_V_aft_attn <- df.resp_V %>%
  filter(subject %in% df.ppts_att_V$subject) #73
